\documentclass[11pt]{article} % hidelinks
\usepackage{titlesec}
\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{longtable, array}
\usepackage{enumitem}
\usepackage{hang}
\usepackage{fontawesome5}
\usepackage[margin=3cm, a4paper]{geometry}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage[
]{biblatex}
\addbibresource{pubs.bib}

\hypersetup{
    colorlinks=true,
    linkcolor=RoyalBlue,
    urlcolor=black,
    citecolor=Fuchsia
}

\titleformat{\section}{\large\scshape}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{1.2em}{1.2em} % Spacing around sections

% 
\newlength{\firstColumnWidth}
\setlength{\firstColumnWidth}{3cm}
\newlength{\tabusep}
\setlength{\tabusep}{6mm}
\newlength{\secondColumnWidth}
\setlength{\secondColumnWidth}{\dimexpr \linewidth-\firstColumnWidth \relax}
\newlength{\slashSize}
\settoheight{\slashSize}{\texttt{/}}
\newcommand{\GitHub}{\raisebox{-0.22ex}{\fontsize{1.5\slashSize}{1.44\slashSize}\ttfamily\faIcon{github}}}

% Longlist, enumerate etc.
\renewcommand\labelitemi{--}
\setlist{nolistsep, noitemsep}
\setlength\parindent{0pt}
\setlength{\hyphenpenalty}{5000}
\setlength{\LTpre}{0pt}
\setlength{\LTpost}{1.2em}
\setlength{\hangingindent}{9mm}
\newcommand{\tabitem}{~~\llap{--}~~}
\newcommand{\threeecols}[2]{\parbox{
    0.98\secondColumnWidth}{\hfill
    \parbox[t]{0.465\secondColumnWidth}{#1}
    \parbox[t]{0.465\secondColumnWidth}{#2}
    }
}

%\usepackage{showframe}

\newcommand{\Tr}[1]{\textturkish{#1}}
\newcommand{\tnl}{\tabularnewline & \tabularnewline}

% Font Stuff
\usepackage{libertinus-otf}

\setmonofont[
  Scale          = MatchLowercase,
  Path           = {iA-Fonts/iA Writer Quattro/Static/},
  Extension      = .ttf,
  UprightFont    = *-Regular,
  BoldFont       = *-Bold,
  ItalicFont     = *-Italic,
  BoldItalicFont = *-BoldItalic,
  ]{iAWriterQuattroS}

\newcommand\liningnumbers{\addfontfeature{Numbers=Lining}}

\newenvironment{twocols}
    {
    \begin{longtable}[h]{%
        @{}%
        >{\raggedleft}p{\firstColumnWidth}%
        @{\hspace{\tabusep}}%
        >{\arraybackslash\raggedright}p{\dimexpr %
            \linewidth-\firstColumnWidth-\tabusep%
        \relax}%
        @{}%
        }
    } {
        \end{longtable}
    }
    

\newcommand{\subTitle}[1]{\multicolumn{2}{l}{#1}}

% Localisation stuff
\setdefaultlanguage[variant=us]{english}
\setotherlanguage{turkish}


\begin{document}

\begin{center}
	\Tr{\Huge \scshape {Utku Birkan}} \medskip \par
    Mutlukent, 1958. Sk, No:5 \\
    06800, Çankaya / Ankara, TR  \par
	\href{mailto:utku.birkan@gmail.com}{\ttfamily utku.birkan@gmail.com}\\
    \href{https://github.com/kurabirko}{\ttfamily {\GitHub}/kurabirko}\par
\end{center}

\section{Education}

\begin{twocols}
    2018 -- Present & %
        \textbf{BSc Computer Engineering (Double Major)} \\
        Middle East Techinal University -- \textit{Ankara, Turkey} \\
        Cumulative GPA: \liningnumbers{3.77} \tnl
    2017 -- Present & %
            \textbf{BSc Physics} \\
            Middle East Techinal University -- \textit{Ankara, Turkey} \\
            Cumulative GPA: \liningnumbers{3.48}
\end{twocols}

\section{Research Experience}

\begin{twocols}
 2020 -- Present & 
        \textbf{Undergraduate Researcher} (08\kern1pt/2020 -- Present)\\
        \textbf{Research Intern} (07\kern1pt/2020 -- 08\kern1pt/2020)\\
        QWorld Association -- \textit{Lativa}\\
        P.I.: Abuzer Yakaryılmaz, PhD and Özlem Salehi, PhD
        \begin{itemize}
            \item Work on ``Implementing Quantum Finite Automata Algorithms on Noisy Devices'' project as a part of QWorld's QResearch Program.
            \item Study the mathematical modelling of quantum finite automata and their language recognition power for some specific languages.
            \item Investigate architecture specific optimisations for the studied automata.
            \item Conduct experiments using IBM's quantum computers.
            \item Oversee the preparation of project manuscript and poster presentation.
        \end{itemize}
\end{twocols}

\section{Publication}

\fullcite{Birkan2021}
% \printbibliography[heading=none]

\newpage
\section{Professional \& Volunteer Experience}
\begin{twocols}
    2019 -- Present & %
        \textbf{Leading Member} \\
        QTurkey -- \textit{Turkey}
        \begin{itemize}
            \item A part of the \emph{Train the Trainers} education program, developed in cooperation with Microsoft.
            \item Develop Jupyter based education material as a part of the educational committee.
            \item Volunteered as an instructor or a mentor in various “Introduction to Quantum Computing” workshops.
            \item Helped organise a seminar on quantum computing.
        \end{itemize} \tabularnewline
    2018 -- Present & %
        \textbf{Member} \\ 
        METU Life Saving and First Aid Society -- \textit{Turkey}
        \begin{itemize}
            \item Volunteer as an instructor, teaching first aid to the local community and university members.
        \end{itemize}
\end{twocols}

\section{Qualifications}

\begin{twocols}
    Languages & \threeecols{\tabitem Native Turkish}{
    \tabitem Advanced English} \tabularnewline & \tabularnewline
    Computer Skills & %
        Programming Languages\\[.5em]
        \threeecols
            {\tabitem C/C++ \par \tabitem Q\# and QDK \par \tabitem \LaTeX}
            {\tabitem Python \par \tabitem Swift \par \tabitem Haskell}\\[.7em]
        Technologies/Frameworks\\[.3em]
        \threeecols {\tabitem git and Github}{\tabitem Qiskit}
\end{twocols}

\section{Honours, Certificates \& Awards}
\vspace{-.5em}
\renewcommand*{\arraystretch}{1.5}

\begin{twocols}
    2020 & \textbf{First Team Award for the Best Project}, QWorld Association \tabularnewline
    2018 -- Present & \textbf{First Aid License}, Turkish Red Crescent \tabularnewline
    2017 -- Present & \textbf{High Honor List}, Middle East Techincal University \tabularnewline
    2017 -- Present & %
        \textbf{Undergraduate Scholarship Program}, TÜBİTAK (The Scientific and Technological Research Council of Turkey)\\
        Awarded due to high ranking in National University Entrance Examination.
\end{twocols}

\end{document}
