\documentclass[11pt]{article}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage[turkish, english]{babel}
\usepackage{csquotes}
\usepackage{longtable, array}
\usepackage{enumitem}
\usepackage[margin=2cm, a4paper]{geometry}
\usepackage{hyperref}
\usepackage{biblatex}
\addbibresource{pubs.bib}

\hypersetup{
    colorlinks=true,
    allcolors=black,
}

\titleformat{\section}{\large\scshape}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{1.2em}{1.2em} % Spacing around sections


\newlength{\firstColumnWidth}
\setlength{\firstColumnWidth}{3cm}
\newlength{\tabusep}
\setlength{\tabusep}{6mm}
\newlength{\secondColumnWidth}
\setlength{\secondColumnWidth}{\dimexpr \linewidth-\firstColumnWidth \relax}
\newlength{\slashSize}
\settoheight{\slashSize}{\texttt{/}}

% Longlist, enumerate etc.
\renewcommand\labelitemi{--}
\setlist{nolistsep, noitemsep}
\setlength\parindent{0pt}
\setlength{\hyphenpenalty}{5000}
\setlength{\LTpre}{0pt}
\setlength{\LTpost}{1.2em}
\newcommand{\tabitem}{~~\llap{--}~~}
\newcommand{\threeecols}[2]{\parbox{
    0.98\secondColumnWidth}{\hfill
    \parbox[t]{0.465\secondColumnWidth}{#1}
    \parbox[t]{0.465\secondColumnWidth}{#2}
    }
}

%\usepackage{showframe}

\newcommand{\twoNewline}{\tabularnewline & \tabularnewline}

% Font Stuff
\usepackage{libertinus}
\defaultfontfeatures{Scale = MatchLowercase}
\setsansfont{TeX Gyre Heros}
\setmonofont{Latin Modern Mono}

\newcommand\liningnumbers{\addfontfeature{Numbers=Lining}}

\newenvironment{twocols}
    {
    \begin{longtable}[h]{%
        @{}%
        >{\raggedleft}p{\firstColumnWidth}%
        @{\hspace{\tabusep}}%
        >{\arraybackslash\raggedright}p{\dimexpr %
            \linewidth-\firstColumnWidth-\tabusep%
        \relax}%
        @{}%
        }
    } {
        \end{longtable}
    }
    

\newcommand{\subTitle}[1]{\multicolumn{2}{l}{#1}}

% Localisation stuff

\begin{document}

\begin{center}
	{\huge \LibertinusDisplay \foreignlanguage{turkish}{Utku Birkan}} \medskip \par
    Mutlukent, 1958. Sk, No:5, Çankaya / Ankara  \par
	\href{mailto:utku.birkan@gmail.com}{utku.birkan@gmail.com} \hspace{2pt} · \hspace{2pt}
    \href{https://github.com/kurabirko}{github.com/kurabirko}\par
\end{center}

\section{Education}

\begin{twocols}
  2018 -- Present & %
    \textbf{BSc Computer Engineering (Double Major)} \\
    Middle East Techinal University -- \textit{Ankara, Turkey} \\
    Cumulative GPA: \liningnumbers{3.70} \\
    Expected Graduation: July 2023 \twoNewline
  2017 -- Present & %
    \textbf{BSc Physics} \\
    Middle East Techinal University -- \textit{Ankara, Turkey} \\
    Cumulative GPA: \liningnumbers{3.55} \\
    Dissertation: Measurement Based Quantum Computing \\
    Expected Graduation: July 2022
\end{twocols}

\section{Relevant Experience}

\begin{twocols}
  2021 -- Present & 
    \textbf{Mini-Mentorship Program} \\
    Microsoft Quantum -- \textit{United States} \\
    P.I.: Mariia Mykhailova \\
    \begin{itemize}
      \item Develop educational material as a part of Quantum Katas on E91 quantum key distribution protocol.
      \item Write unit tests for Q\# and simulations using QDK. 
    \end{itemize} \tabularnewline
  2020 -- 2021 & 
    \textbf{Undergraduate Researcher} (08/2020 -- 05/2021)\\
    \textbf{Research Intern} (07/2020 -- 08/2020)\\
    QWorld Association -- \textit{Lativa}\\
    P.I.: Abuzer Yakaryılmaz, PhD and Özlem Salehi, PhD
    \begin{itemize}
        \item Worked on “Implementing Quantum Finite Automata Algorithms on Noisy Devices” project as a part of QWorld's QResearch Program.
        \item Studied the mathematical modelling of quantum finite automata and their language recognition power for some specific languages.
        \item Investigated architecture specific optimisations for the studied automata.
        \item Conducted experiments using IBM's quantum computers.
        \item Oversaw the preparation of project manuscript and poster presentation.
    \end{itemize} \tabularnewline
    2019 -- Present & 
    \textbf{Instructor and Leading Member} \\
    QTurkey -- \textit{Turkey}
    \begin{itemize}
        \item Work as an instructor in various quantum algorithms workshops.
        \item Participated in the \emph{Train the Trainers} education program as an educator and worked in cooperation with Microsoft.
        \item Developed Jupyter based education material as a part of the educational committee.
        \item Helped organise a seminar on quantum computing.
    \end{itemize}
\end{twocols}

\section{Publication}

\fullcite{Birkan2021}
% \printbibliography[heading=none]

\section{Skills}

\begin{twocols}
    Languages & Turkish, English \twoNewline
    Programming & C++, Python, Microsoft Q\# and QDK, git, \LaTeX, IBM Qiskit
\end{twocols}

\section{Honours, Certificates \& Awards}
\vspace{-.5em}
\renewcommand*{\arraystretch}{1.5}

\begin{twocols}
    2020 & \textbf{First Team Award for the Best Project}, QWorld Association \tabularnewline
    2018 -- Present & \textbf{First Aid License}, Turkish Red Crescent \tabularnewline
    2017 -- Present & \textbf{High Honor List}, Middle East Techincal University \tabularnewline
    2017 -- 2021 & %
        \textbf{Undergraduate Scholarship Program}, TÜBİTAK (The Scientific and Technological Research Council of Turkey)\\
        Awarded due to high ranking in National University Entrance Examination.
\end{twocols}

\section{Membership}
\begin{twocols}
    2018 -- Present & %
    \textbf{Member} \\ 
    METU Life Saving and First Aid Society -- \textit{Turkey}
    \begin{itemize}
        \item Volunteer as an instructor, teaching first aid to the local community and university members.
    \end{itemize}
\end{twocols}


\end{document}
